
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{José}{ Gonzales}{Senior business analyst \& PM} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
+57 (313) 868 6693
jzgonzales@gmail.com
skype: jose.gonzales
\section{Languages}
Spanish native
English B2
Portuguese basic
\section{Soft skills}
Adaptability {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
Critical thinking {\color{bullet} $\bullet$ $\bullet$ $\bullet$}
Empathy {\color{bullet} $\bullet$ $\bullet$ $\bullet$}
Negotiation {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
Strategy {\color{bullet} $\bullet$ $\bullet$ $\bullet$}
\section{Tech skills}
.NET {\color{white} \color{bullet} $\bullet$ $\bullet$ $\bullet$}
Apache Hadoop {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
Datacenter {\color{bullet} $\bullet$ $\bullet$ $\bullet$}
Data networks {\color{white} \color{bullet} $\bullet$ $\bullet$ $\bullet$}
GIT {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
IoT {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
JAVA {\color{white} $\bullet$ $\bullet$ \color{bullet} $\bullet$}
Linux {\color{white} \color{bullet} $\bullet$ $\bullet$ $\bullet$}
Oracle {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
SAP {\color{white} $\bullet$ \color{bullet} $\bullet$ $\bullet$}
SQL {\color{bullet} $\bullet$ $\bullet$ $\bullet$}
\end{aside}

\section{Qualifications Profile}
\flushleft
Bilingual spanish-english senior project manager and senior business analyst, software architect and experienced software engineer, systems engineer with proven and wide experience in design and direction of both software and infrastructure projects. Strong background in architecture and deploy of enterprise solutions, technical team leader in highly technical and complex environments.\\
Owner of a deep understanding of the full software life-cycle processes from requirements gathering, design, coding and testing to integration and deploy. Comprehensive understanding of IT processes, curious, systematic, critical and pragmatic, client focused, experienced as director and business manager with a solid financial and commercial awareness.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2016--2017}
{Project Management Certificate{\normalfont }}
{The University of Texas at Arligton}
{\emph{}}

%------------------------------------------------

\entry
{2010--2015}
{Computer systems engineering {\normalfont}}
{Politécnico Grancolombiano, Bogotá}
{}

%------------------------------------------------

\entry
{2007--2011}
{Mathematics {\normalfont unfinished}}
{Politécnico Grancolombiano, Bogotá}
{}

%------------------------------------------------
\entry
{2006--2008}
{Systems administrator {\normalfont}}
{Politécnico Grancolombiano, Bogotá}
{}

%------------------------------------------------

\entry
{1996 - 1998}
{Business administration {\normalfont unfinished}}
{Universidad Externado de Colombia, Bogotá}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Profesional experience}

\subsection{Part Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2017--Now}
{Independent product designer}
{Bogotá}
{\emph{\textsuperscript{}Arduino project developer } \\
Designer of a preschool mathematics teaching game based on Cuisenaire rods. The project involved the construction of a prototype using Arduino micro-architecture platform.\\
}
%------------------------------------------------
\entry
{2017--Now}
{Independent product designer}
{Bogotá}
{\emph{\textsuperscript{}IoT Arduino project developer } \\
Designer of a home e-gardening prototype platform over Arduino and PHP Symfony 3 Backoffice.\\
}
%------------------------------------------------
\entry
{2017}
{SCH Consultores - consultant}
{Caracas}
{\emph{\textsuperscript{}Hyper-Inflation software consultant } \\
IAS-29 .NET Software maintenance technical leader, SQL Server 2012 database Scheme adjustments. \\
}
%------------------------------------------------
\newpage

\begin{entrylist}

\entry
{Oct 2016}
{Apache hadoop specification engineer - Consultant}
{Bogotá}
{\emph{Project: UIAF - SIREL} \\
The project scope was to re-design current SIREL Platform in order to take advantage of Apache Hadoop BigData technologies and Python dJango as framework of the front layer. SIREL was redesigned to work as a front layer of a Hadoop cluster. My role was to specify the system requirements.}

\end{entrylist}

\subsection{Full Time}

\begin{entrylist}

\entry
{Apr-Jun 2016}
{THT - THE TALENT SYSTEM}
{Bogotá}
{\emph{IT Director - Interim} \\
Some of my responsibilities and achievements were:
\begin{itemize}
\item Analise business scenarios and found technical flaws.
\item Propose a model to re-restructure the IT department.
\item Lead the IT team to reach company's objectives during transition.
\item Propose and execute the software testing procedures.
\item Assure and maintain 7x24 availability of the core business platform to customers in Latin and Central America. The platform was built over .NET technologies: WebForms, SQL Server 2012 and Telerik controls.
\item Co-designer and executor of the security schema for the set of .NET applications operating from the RackSpace public cloud. This includes the implementation of the following technologies
\begin{itemize}
\item Brocade Vyatta firewall.
\item VPN tunnel over SSL.
\item NAT network to hide public IP addressing
\end{itemize}
\end{itemize}

}
\\

\entry
{Oct-Mar 2015/16}
{PROCESOS Y SERVICIOS - Private consultant}
{Bogotá}
{\emph{Project: Sistema documental y de información pensional SENA} \\
\emph{Role: Software component technical coordinator} \\
The SENA -Servicio Nacional de Aprendizaje- request the implementation of a EDMS - Electronic digital document management system. The project scope involved 2 stages, 1) files document digitalization 2)Software implementation. My role was to perform as technical coordinator of the software component. Some of my responsibilities and achievements:
\begin{itemize}
\item Resposible for analyzing, capturing and priorizing the customer requirements for:
\begin{itemize}
\item Calculos Actuariales - Treasury report.
\item RUAF report - Ministry of health.
\item Legal department BPM module .
\end{itemize}
\item Contributor of the HLD - High level design - of the platform restricted to .NET technologies IIS 8.x, Linq, MS SQL Server, Entity Framework and Syncfusion .NET controls.
\item Database model co-designer.
\item Design and deploy infrastructure environments:
\begin{itemize}
\item Cloud model (pre-production environment).
\item On-Premises model (production environment).
\end{itemize}
\item Trainer of customer system administrators.
\item Trainer of system users.
\item Technical representative to project committee.
\end{itemize}

}

\end{entrylist}

\newpage

\section{Courses}

\begin{entrylist}

%------------------------------------------------

\entry
{2017}
{Project management certificate}
{The University of Texas at Arlington}
{}

\entry
{2016}
{Big Data Specialisation}
{Coursera, University of San Diego}
{}

\entry
{2013}
{The Lean startup methodology}
{Colegio superior de estudios en administración}
{Entrepreneurship program Apps.co of Ministry of technology MINTIC, finalist project.}

\entry
{2012}
{IBM System-i Administration}
{IBM de Colombia, Eclosión}
{Grant Plan becarios IBM 2012}

\entry
{2012}
{IBM Rational software lifecycle tools}
{IBM de Colombia, Fundación Compuclub}
{}

\entry
{2011}
{IBM DB2 Fundamentals}
{IBM de Colombia, Universidad Nacional de Colombia}
{Tutor Raul Chong}

\entry
{2008}
{Implementing and maintaining SQL Server 2008}\
{Fundación compuclub}
{}

\entry
{2008}
{Implementing and maintaining SQL Server 2008 Analysis services}\
{Fundación compuclub}
{}

\entry
{2008}
{Implementing and maintaining SQL Server 2008 Reporting services}\
{Fundación compuclub}
{}

\entry
{2007}
{Implementing Microsoft office Sharepoint Server 2007}\
{Fundación compuclub}
{}

\entry
{2006}
{Implementing Microsoft SQL server 2005}
{Fundación compuclub}
{}

\entry
{2006}
{Java EE 5}
{Fundación compuclub}
{}

\entry
{2006}
{Java J2SE 5.0}
{Fundación compuclub}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Social contribution}

\begin{entrylist}

%------------------------------------------------

\entry
{2011}
{Oral Presentation}
{California Business Conference}
{Presented the research I conducted for my Masters of Commerce degree.}

%------------------------------------------------

\entry
{2010}
{Poster}
{Annual Business Conference, Oregon}
{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running


\end{document}